Notes on Design and Implementation of Anglican

### 2015-07-19 paper/paper.tex
better english

Anglican is implemented in just this way --- a macro facility
provided by Clojure, a Lisp dialect, is used both to add to
Clojure constructs that delimit probabilistic, rather than
deterministic, code, and to alter the operational semantics of
Clojure expressions inside probabilistic code fragments. Anglican
claims its right to count as a separate language because of the
ubiquitous probabilistic execution semantics rather than because
of a different syntax, which is actually an advantage rather
than a drawback --- Clojure programmers only need to know how to
specify the boundaries of Anglican programs, but can use
familiar Clojure syntax to write probabilistic code.

>>>>

Anglican is implemented in just this way --- a macro facility
provided by Clojure, a Lisp dialect, is used both to extend
Clojure with constructs that delimit probabilistic code, and to
alter the operational semantics of Clojure expressions inside
probabilistic code fragments. Anglican claims its right to count
as a separate language because of the ubiquitous probabilistic
execution semantics rather than because of a different syntax,
which is actually an advantage rather than a drawback ---
Clojure programmers only need to know how to specify the
boundaries of Anglican programs, but can use familiar Clojure
syntax to write probabilistic code.
